---
title: "German-ShockSimulation"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

Influence vectors v are calculated as $v =(1/n) (I-(1-\alpha)W)^{-1}\mathbf{1}$
with $\alpha =0.3333$ (choice in Acemoglu(2012)).


Acemoglu (2017) calculate Domar weights of a networked economy in two different ways. One is with sales data, dividing industries sales over GDP. This is an empirical Domar weight. The other way is as in the above equation.


```{r}

source("./code/1_3_readAndRunOutdegrees.R")

the_data <- readrun_matrices("DE", "shock", order=1)


# for US??
source("./code/2_1_simulate_shocks.R")

shocked_Economies <- simulate_shocks(the_data[[1]][[1]], "laplace", the_data[[2]], n_shocks = 10^3)

shocked_Economies_normal <- simulate_shocks(the_data[[1]][[1]], "normal", the_data[[2]], n_shocks = 10^3)


```




### 1 Laplacian (double exponential) shocks

All time series are plotted on the same interval of the y-axis to illustrate how volatile aggregate output in different economies is in comparison to shocks. As expected from the analytic statements, volatility is smoothed strongest in the homogeneous economy. Volatility doesn't vanish so fast in the networked economy.


```{r shock-timeseries}

library(ggplot2)
library(ggExtra)
#library(ggridges)
# https://hydroecology.net/plotting-marginal-distributions-redux/


ylimits <- max(shocked_Economies$Shocks$Shocks)
p1 <- ggplot(data=shocked_Economies$Shocks, aes(timestep, Shocks)) + geom_point(alpha=0) + geom_line() + theme_minimal() + annotate("text", x = length(shocked_Economies$Shocks$Shocks) * (1/4), y = -ylimits, label =  paste("sd = ", round(sd(shocked_Economies$Shocks[["Shocks"]]), digits = 3))) + ylim(c(-ylimits,ylimits)) # suppress points, only show lines

ggMarginal(p1, margins="y", type = "histogram", fill=NA) #type="density"
# https://stackoverflow.com/questions/60279826/add-marginal-density-plot-based-on-subset-of-plotted-data
# https://github.com/daattali/ggExtra/issues/109


```



```{r timeseries_AggOut_homogenousEconomy}


p1 <- ggplot(data=shocked_Economies$shock_output, aes(timestep, homogeneousEconomy)) + geom_point(alpha=0) + geom_line() + theme_minimal() + annotate("text", x = length(shocked_Economies$shock_output$timestep) * (1/6) , y = -ylimits*0.9, label =  paste("sd = ", round(sd(shocked_Economies$shock_output[["homogeneousEconomy"]]), digits = 3))) + ylim(c(-ylimits,ylimits)) # suppress points, only show lines
ggMarginal(p1, margins="y", type = "histogram", fill=NA) #type="density"
# https://stackoverflow.com/questions/60279826/add-marginal-density-plot-based-on-subset-of-plotted-data
# https://github.com/daattali/ggExtra/issues/109


# calculate predicted volatility
predicted_stddev_homog_laplace <- (1/ sqrt(71)) * sd(shocked_Economies$Shocks[["Shocks"]])


```

The standard deviation predicted by the analytical results is `r predicted_stddev_homog_laplace`.

Volatility of aggregate output in networked economy has decreased compared to shocks but is higher than in homogenous economy. Due to the law of large numbers, the more disaggregated the economy gets (n_sectors --> $\infty$) the lower should be the volatility. With more sectors, the aggregate output time series will center narrower and narrower around the mean.


```{r timeseries_AggOut_networkedEconomy}


p1 <- ggplot(data=shocked_Economies$shock_output, aes(timestep, networkedEconomy)) + geom_point(alpha=0) + geom_line() + theme_minimal() + annotate("text", x = length(shocked_Economies$shock_output$timestep) * (1/6), y = -ylimits*0.9, label =  paste("sd = ", round(sd(shocked_Economies$shock_output[["networkedEconomy"]]), digits = 3))) + ylim(c(-ylimits,ylimits)) # suppress points, only show lines
ggMarginal(p1, margins="y", type = "histogram", fill=NA) #type="density"
# https://stackoverflow.com/questions/60279826/add-marginal-density-plot-based-on-subset-of-plotted-data
# https://github.com/daattali/ggExtra/issues/109


# is it fat tailed? check QQ-plot

# calculate predicted volatility
predicted_stddev_netw_laplace <- (shocked_Economies$euklidian_norm_v_tibble$networkedEconomy) * sd(shocked_Economies$Shocks[["Shocks"]])


```

The standard deviation predicted by the analytical results with the influence vector v is `r predicted_stddev_netw_laplace`.


```{r timeseries_AggOut_heterogenousNetworkedEconomy}

p1 <- ggplot(data=shocked_Economies$shock_output, aes(timestep, heterogeneousnetworkedEconomy)) + geom_point(alpha=0) + geom_line() + theme_minimal() + annotate("text", x = length(shocked_Economies$shock_output$timestep) * (1/6), y = -ylimits*0.9, label =  paste("sd = ", round(sd(shocked_Economies$shock_output[["heterogeneousnetworkedEconomy"]]), digits = 3))) + ylim(c(-ylimits,ylimits)) # suppress points, only show lines
ggMarginal(p1, margins="y", type = "histogram", fill=NA) #type="density"
# https://stackoverflow.com/questions/60279826/add-marginal-density-plot-based-on-subset-of-plotted-data
# https://github.com/daattali/ggExtra/issues/109


# is it fat tailed? check QQ-plot

# calculate predicted volatility
predicted_stddev_hetnetw_laplace <- (shocked_Economies$euklidian_norm_v_tibble$heterogeneousnetworkedEconomy) * sd(shocked_Economies$Shocks[["Shocks"]])





```
The standard deviation of aggregate output is even larger than the standard deviation of shocks when the influence vector is the sum of output shares and output multipliers.



#### 1.1 Q-Q plots aggregate output and laplacian shocks

With too low shock sample size aggregate output appears to be less normal distributed than shocks.

[x- und y-Achse muss überall selbe skalierung haben um optisch den Vergleich zwischen den QQ-plots zu haben]: The shocks are divided by the euclidean norm of the influence vector v. This scales shocks in each type of economy to the same interval.


As expected from the analytical results, aggregate output of the networked economy deviates more from the normal distribution in the tails than aggregate output of the homogeneous economy.

```{r QQ-plot_networkedVSshocks, fig.show="hold", out.width="50%"}

#fluctuations <- bind_cols(list(out_agg = out_agg, shocks = Shocks[1,]))

ggplot(data = shocked_Economies$shock_output, aes(sample=networkedEconomy* (1/shocked_Economies$euklidian_norm_v_tibble$networkedEconomy))) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("networked")
ggplot(data = shocked_Economies$Shocks, aes(sample=Shocks)) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("shocks")


```




```{r QQ-plot_homogenousVSshocks, fig.show="hold", out.width="50%"}

ggplot(data = shocked_Economies$shock_output, aes(sample=homogeneousEconomy* (1/shocked_Economies$euklidian_norm_v_tibble$homogeneousEconomy))) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("homogeneous")
ggplot(data = shocked_Economies$Shocks, aes(sample=Shocks)) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("shocks")

```



```{r QQ-plot_heterogeneousnetworkedVSshocks, fig.show="hold", out.width="50%"}

#fluctuations <- bind_cols(list(out_agg = out_agg, shocks = Shocks[1,]))

ggplot(data = shocked_Economies$shock_output, aes(sample=heterogeneousnetworkedEconomy* (1/shocked_Economies$euklidian_norm_v_tibble$heterogeneousnetworkedEconomy))) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("heterogeneousnetworked")
ggplot(data = shocked_Economies$Shocks, aes(sample=Shocks)) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("shocks")


```


### 2 Normal shocks

```{r shock-timeseries_normal}

library(ggplot2)
library(ggExtra)
#library(ggridges)
# https://hydroecology.net/plotting-marginal-distributions-redux/
'ggplot(data= shocked_Economies$shock_output , aes(timestep, networkedEconomy)) + geom_line() + 
  geom_vridgeline(data = res.select, aes(group = time, width = ..density..), 
                  stat = "ydensity", scale = 5000, fill = NA, color = "blue", size = 1) '

#ggplot(data=shocked_Economies$shock_output, aes(timestep, networkedEconomy)) + geom_point() + geom_line()

ylimits <- max(shocked_Economies_normal$Shocks$Shocks)
p1 <- ggplot(data=shocked_Economies_normal$Shocks, aes(timestep, Shocks)) + geom_point(alpha=0) + geom_line() + theme_minimal() + annotate("text", x = length(shocked_Economies_normal$Shocks$Shocks) * (1/4), y = -ylimits, label =  paste("sd = ", round(sd(shocked_Economies_normal$Shocks[["Shocks"]]), digits = 3))) + ylim(c(-ylimits,ylimits)) # suppress points, only show lines
ggMarginal(p1, margins="y", type = "histogram", fill=NA) #type="density"
# https://stackoverflow.com/questions/60279826/add-marginal-density-plot-based-on-subset-of-plotted-data
# https://github.com/daattali/ggExtra/issues/109

```


```{r timeseries_AggOut_homogenousEconomy_normal}


p1 <- ggplot(data=shocked_Economies_normal$shock_output, aes(timestep, homogeneousEconomy)) + geom_point(alpha=0) + geom_line() + theme_minimal() + annotate("text", x = length(shocked_Economies_normal$shock_output$timestep) * (1/6) , y = -ylimits*0.9, label =  paste("sd = ", round(sd(shocked_Economies_normal$shock_output[["homogeneousEconomy"]]), digits = 3))) + ylim(c(-ylimits,ylimits)) # suppress points, only show lines
ggMarginal(p1, margins="y", type = "histogram", fill=NA) #type="density"
# https://stackoverflow.com/questions/60279826/add-marginal-density-plot-based-on-subset-of-plotted-data
# https://github.com/daattali/ggExtra/issues/109


# calculate predicted volatility
predicted_stddev_homog_normal <- (1/ sqrt(71)) * sd(shocked_Economies_normal$Shocks[["Shocks"]])


```


The standard deviation predicted by the analytical results is `r predicted_stddev_homog_normal`.


```{r timeseries_AggOut_networkedEconomy_normal}


p1 <- ggplot(data=shocked_Economies_normal$shock_output, aes(timestep, networkedEconomy)) + geom_point(alpha=0) + geom_line() + theme_minimal() + annotate("text", x = length(shocked_Economies_normal$shock_output$timestep) * (1/6), y = -ylimits*0.9, label =  paste("sd = ", round(sd(shocked_Economies_normal$shock_output[["networkedEconomy"]]), digits = 3))) + ylim(c(-ylimits,ylimits)) # suppress points, only show lines
ggMarginal(p1, margins="y", type = "histogram", fill=NA) #type="density"
# https://stackoverflow.com/questions/60279826/add-marginal-density-plot-based-on-subset-of-plotted-data
# https://github.com/daattali/ggExtra/issues/109


# is it fat tailed? check CCDF
# QQ-plot

# predicted standard deviation
predicted_stddev_netw_normal <- (shocked_Economies_normal$euklidian_norm_v_tibble$networkedEconomy) * sd(shocked_Economies_normal$Shocks[["Shocks"]])


```

Using the lower bound approximation of the influence vector v, only including the direct and first order effects, the predicted standard deviation is . And for the influence vector v with all higher order effects: `r predicted_stddev_netw_normal`.



```{r timeseries_AggOut_heterogeneousnetworkedEconomy_normal}


p1 <- ggplot(data=shocked_Economies_normal$shock_output, aes(timestep, heterogeneousnetworkedEconomy)) + geom_point(alpha=0) + geom_line() + theme_minimal() + annotate("text", x = length(shocked_Economies_normal$shock_output$timestep) * (1/6), y = -ylimits*0.9, label =  paste("sd = ", round(sd(shocked_Economies_normal$shock_output[["heterogeneousnetworkedEconomy"]]), digits = 3))) + ylim(c(-ylimits,ylimits)) # suppress points, only show lines
ggMarginal(p1, margins="y", type = "histogram", fill=NA) #type="density"
# https://stackoverflow.com/questions/60279826/add-marginal-density-plot-based-on-subset-of-plotted-data
# https://github.com/daattali/ggExtra/issues/109


# is it fat tailed? check CCDF
# QQ-plot

# predicted standard deviation
predicted_stddev_hetnetw_normal <- (shocked_Economies_normal$euklidian_norm_v_tibble$heterogeneousnetworkedEconomy) * sd(shocked_Economies_normal$Shocks[["Shocks"]])


```

#### 2.1 Q-Q plots aggregate output and normal shocks

```{r QQ-plot_networkedVSshocks_normal, fig.show="hold", out.width="50%"}

#fluctuations <- bind_cols(list(out_agg = out_agg, shocks = Shocks[1,]))

ggplot(data = shocked_Economies_normal$shock_output, aes(sample=networkedEconomy* (1/shocked_Economies_normal$euklidian_norm_v_tibble$networkedEconomy))) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("networked")
ggplot(data = shocked_Economies_normal$Shocks, aes(sample=Shocks)) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("shocks")


```




```{r QQ-plot_homogenousVSshocks_normal, fig.show="hold", out.width="50%"}

ggplot(data = shocked_Economies_normal$shock_output, aes(sample=homogeneousEconomy* (1/shocked_Economies_normal$euklidian_norm_v_tibble$homogeneousEconomy))) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("homogeneous")
ggplot(data = shocked_Economies_normal$Shocks, aes(sample=Shocks)) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("shocks")

```


```{r QQ-plot_heterogeneousnetworkedVSshocks_normal, fig.show="hold", out.width="50%"}

ggplot(data = shocked_Economies_normal$shock_output, aes(sample=heterogeneousnetworkedEconomy* (1/shocked_Economies_normal$euklidian_norm_v_tibble$heterogeneousnetworkedEconomy))) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("heterogeneousnetworked")
ggplot(data = shocked_Economies_normal$Shocks, aes(sample=Shocks)) + geom_qq() + geom_qq_line() + theme_minimal() + ggtitle("shocks")

```


```{r table_shock_volatility}

shockdistr <- c("normal", "laplace")
shocks <- c(sd(shocked_Economies_normal$Shocks[["Shocks"]]), sd(shocked_Economies$Shocks[["Shocks"]]))
homogeneous <- c(predicted_stddev_homog_normal, predicted_stddev_homog_laplace)
networked <- c(predicted_stddev_netw_normal, predicted_stddev_netw_laplace)
heterogeneousnetworked <- c(predicted_stddev_hetnetw_normal, predicted_stddev_hetnetw_laplace)


shock_volatility <- tibble::tibble(shockdistr, shocks, homogeneous, networked, heterogeneousnetworked)
print(shock_volatility)

```


```{r, comment=NA}

library(xtable)
xtable(shock_volatility, type = "latex")

```



#### 3. influence vector v CCDF

```{r plot_v_CCDF}

CCDFs <- shocked_Economies_normal$v %>% map(sort, decreasing=TRUE) %>% as_tibble()
CCDFs["CCDF"] <- (1:length(CCDFs$homogeneousEconomy))/length(CCDFs$homogeneousEconomy)

CCDFs_long <- CCDFs %>% pivot_longer(1:3, values_to = "v", names_to = "heterogeneity")

ggplot(data=CCDFs_long) + geom_point(aes(log(v),log(CCDF), color=heterogeneity)) + theme_minimal()

```

Calculate the statistic delta indicating tail risk.

```{r delta_tailrisk}

delta_homog <- max(shocked_Economies_normal$v$homogeneousEconomy)/(shocked_Economies$euklidian_norm_v_tibble$homogeneousEconomy/sqrt(71))

delta_net <- max(shocked_Economies_normal$v$networkedEconomy)/(shocked_Economies$euklidian_norm_v_tibble$networkedEconomy/sqrt(71))

delta_hetnet <- max(shocked_Economies_normal$v$heterogeneousnetworkedEconomy)/(shocked_Economies$euklidian_norm_v_tibble$heterogeneousnetworkedEconomy/sqrt(71))

delta_homog
delta_net
delta_hetnet


delt <- tibble(homogeneous = delta_homog, networked = delta_net, heterogeneousnetworked = delta_hetnet)
library(xtable)
xtable(delt, type = "latex")

```

