---
title: "US first order outdegrees"
output: github_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```


```{r, echo=FALSE, message=FALSE}

#https://stackoverflow.com/questions/38138307/is-it-possible-to-host-interactive-r-markdown-files-on-github-pages


  source("/media/lukas/77F9-5B63/Studium/Biophysical Production Network/Daten/IO-Deutschland/1_3_readAndRunOutdegrees.R")

#yearsUS <- c(1972, 1977, 1982, 1987, 1992, 1997, 2002)
#yearsDE <- c(2015, 2016, 2017)


years=c(1972, 1977, 1982, 1987, 1992, 1997, 2002)
#years=2002
bs=TRUE
returnedL <- readrun_matrices("US", years, bs)
Result_tables <- returnedL[[1]]
OutdegreesCCDF_nested <- returnedL[[2]]

```

Year: `r years`



```{r, echo=FALSE, eval=FALSE}

source("/media/lukas/77F9-5B63/Studium/Biophysical Production Network/Daten/IO-Deutschland/1_1_nestings_CCDFs.R")

OutdegreesCCDF_nested <- W %>% nesting_normalisingCCDFs(0,0,1)

```



```{r, echo=FALSE, eval=FALSE}

OutdegreesCCDF_nested_15 <- OutdegreesCCDF_nested %>% filter(year==2015)
#OutdegreesCCDF_nested_0297 <- OutdegreesCCDF_nested %>% filter(year %in% c(1997,2002))

source("/media/lukas/77F9-5B63/Studium/Biophysical Production Network/Daten/IO-Deutschland/1_2_estimations_outdegree_smaller.R")

# bs = TRUE activates bootstrapping GoF p-values of distributions 
Result_tables <- estimate_outdegree(OutdegreesCCDF_nested_15, bs=FALSE)


#print(Result_tables)


```


$~$

### Fitted distributions parameters

The following table contains the estimated slope of the tail with different models. The standard error of the two linear regressions differ so much because the corrected regression also uses an upward corrected standard error. Also the p-value of a goodness-of-fit test via bootstrapping for the powerlaw is reported. A high p-value indicates that the distribution is a good fit to to the data.

```{r}

if (bs == TRUE){
  # mit bootstrap
  print(Result_tables[[2]][, c(1:5,7)] %>% filter(distribution %in% c("lm", "lm_GIcorrect",  "ksr", "powerlaw", "powerlaw_exogcut")), n=50)
  
}

if (bs == FALSE){
  # ohne bootstrap
  print(Result_tables[[2]][, c(1:5)] %>% filter(distribution %in% c("lm", "lm_GIcorrect",  "ksr", "powerlaw", "powerlaw_exogcut")), n=50)
}

```


GI corrected linear Regression outputs Acemoglu (2012):

```{r, message=FALSE, echo=FALSE}
# compare to estimated parameters of Acemoglu 2012:

setwd("/media/lukas/77F9-5B63/Studium/Biophysical Production Network/Outputmultiplier/Acemoglu2012_NetworkOriginsOfAggregate_9623_data_and_programs_0")

library(readr)

mle_outd1 <- read_csv("mle_outd1.csv", col_names=FALSE)
names(mle_outd1) <- as.character(years)
mle_outd1 <- mutate(mle_outd1, parameter= c("slope", "stderror", "tail-length"), .before = "1972")




nwslope_outd1 <- read_csv("nwslope_outd1.csv", col_names=FALSE)
names(nwslope_outd1) <- as.character(years)
#nwslope_outd1 <- mutate(mle_outd1, parameter= c("slope", "stderror", "tail-length"), .before = "1972")




ols_gi_outd1 <- read_csv("ols_gi_outd1.csv", col_names=FALSE)
names(ols_gi_outd1) <- as.character(years)
ols_gi_outd1 <- mutate(ols_gi_outd1, parameter= c("slope", "stderror"), .before = "1972")

print(ols_gi_outd1)

```

NW Kernel Regression slope Acemoglu (2012): 

```{r, echo=FALSE}

print(nwslope_outd1)

```


MLE power law outputs Acemoglu (2012):

```{r, echo=FALSE}

print(mle_outd1)

```




$~$

$~$


### Comparing GoF of alternative distributions to power law

P-values of the one sided likelihood ratio tests. The powerlaw of 2 different tail lengths is compared to the lognormal, weibull and exponential distribution (each estimated with the tail length corresponding to the powerlaw they are compared to). The p-value is the probability of having the test statistic tending to one distribution if actually the other distribution is a better fit. Thus the high p-values for lognormal and weibull indicates that the tendency of the test statistic to one distribution is not significant. The p-value for the exponential distribution is low, therefore the positive test statistic (1.9 and 1.6) tells that the powerlaw is a significantly better fit.



```{r}

print(Result_tables[[5]])

Result_tables[[4]]$exponential[[1]]$test_statistic
Result_tables[[4]]$exponential[[2]]$test_statistic

```

P-values of two sided likelihood ratio tests. The p-values are the probability of getting a positive or negative test statistic with this value if actually no distribution fits better. The p-values for lognormal and weibull are large, therefore the test can not distinguish whether the power law or these distributions fit better. Because the p-value for the exponential distribution is low, the positive test statistic tells that the power law is a significantly better fit than the exponential.


```{r}

print(Result_tables[[6]])

```


```{r, echo=FALSE, eval=FALSE}

library(xtable)

# https://tex.stackexchange.com/questions/25575/how-can-i-use-a-table-generated-by-r-in-latex
xtable(Result_tables[[2]][,1:5] %>% filter(distribution %in% c("lm", "lm_GIcorrect", "powerlaw", "powerlaw_exogcut")), type = "latex")

# weibull and lognormal have tow parameters and exponential one which doesn't compare well to slope of lm, so I don't report them

```

$~$

### Empirical CCDF 2002 first order outdegrees

```{r, message=FALSE}

library(ggplot2)


ggplot(data = (OutdegreesCCDF_nested %>% filter(year==years[length(years)]) %>% .$outdCCDF %>% .[[1]])) + geom_point(, mapping = aes(x=outdegree, y=CCDF), shape=1) + geom_density(aes(x=outdegree), colour="tomato2") + theme_minimal()

```


$~$

$~$

### Plots of fitted distributions versus fitted power law (2002)
#### Linear Regression (left) and linear regression with GI correction (right) versus power law (20% tail)

```{r, echo=FALSE, results='hide', fig.show="hold", out.width="50%"}


ggplot() + geom_point(data = (OutdegreesCCDF_nested %>% filter(year=="2002") %>% .$outdCCDF %>% .[[1]]), mapping = aes( x=log(outdegree), y=log(CCDF)), shape=1) + 
  geom_line(data = (Result_tables[[1]] %>% filter(year=="2002") %>% filter(distribution %in% c("lm", "powerlaw_exogcut"))) , mapping = aes(x=log(x), y=log(y), color=distribution, linetype=distribution)) + theme_minimal() #+ ylim(-7.5,0)

ggplot() + geom_point(data = (OutdegreesCCDF_nested %>% filter(year=="2002") %>% .$outdCCDF %>% .[[1]]), mapping = aes( x=log(outdegree), y=log(CCDF)), shape=1) + 
  geom_line(data = (Result_tables[[1]] %>% filter(year=="2002") %>% filter(distribution %in% c("lm_GIcorrect", "powerlaw_exogcut"))) , mapping = aes(x=log(x), y=log(y), color=distribution, linetype=distribution)) + theme_minimal() #+ ylim(-7.5,0)




# To do:
#Include the standard deviation of the lm slope by adding a custom ribbon:
#https://stackoverflow.com/questions/14636052/using-smooth-in-ggplot2-to-fit-a-linear-model-using-the-errors-given-in-the-data
#https://stackoverflow.com/questions/4205428/show-standard-devation-using-geom-smooth-and-ggplot
#https://www.r-graph-gallery.com/104-plot-lines-with-error-envelopes-ggplot2.html

'1.3653409 - 0.0169343
1.3653409 + 0.0169343

slope = (y_end - y_start)/(x_end - x_start)
#ganz viele kleine Dreiecke
# umdrehen zu ansteigend
# dann ist y_startwert bekannt und y_endwert gesucht

y_end = slope*(x_end - x_start) + y_start

yy <- Result_tables[[1]] %>% filter(year==2002) %>% 
  filter(distribution == "lm") %>% .$y %>% unname() %>% log()
y <- c(yy[1])
x <- Result_tables[[1]] %>% filter(year==2002) %>% 
  filter(distribution == "lm") %>% .$x %>% log()

slope = 1.3653409 - 0.0169343
for (i in 2:length(x)){
  y[i] = slope*(x[i] - x[i-1]) + y[i-1]
  
}'


```


$~$

$~$

#### Kernel Smoothing Regression and power law (20% tail)
```{r}

ggplot() + geom_point(data = (OutdegreesCCDF_nested %>% filter(year=="2002") %>% .$outdCCDF %>% .[[1]]), mapping = aes( x=log(outdegree), y=log(CCDF)), shape=1) + 
  geom_line(data = (Result_tables[[1]] %>% filter(year=="2002") %>% filter(distribution %in% c("ksr", "powerlaw_exogcut"))) , mapping = aes(x=log(x), y=log(y), color=distribution, linetype=distribution)) + theme_minimal() #+ ylim(-7.5,0)

```

$~$

$~$

#### Exponential distribution and power law (20\% tail, left, and optimal tail length, right)

```{r, fig.show="hold", out.width="50%"}

WO_nested <- OutdegreesCCDF_nested %>% unnest(cols = c(outdCCDF))

ggplot() + geom_point(data = (OutdegreesCCDF_nested %>% filter(year=="2002") %>% .$outdCCDF %>% .[[1]]), mapping = aes( x=log(outdegree), y=log(CCDF)), shape=1) + 
  geom_line(data = (Result_tables[[1]] %>% filter(year=="2002") %>% filter(distribution %in% c("exponential_exogcut", "powerlaw_exogcut"))) , mapping = aes(x=log(x), y=log(y), color=distribution, linetype=distribution)) + theme_minimal() + ylim(-7.5,0)


ggplot() + geom_point(data = (OutdegreesCCDF_nested %>% filter(year=="2002") %>% .$outdCCDF %>% .[[1]]), mapping = aes( x=log(outdegree), y=log(CCDF)), shape=1) + 
  geom_line(data = (Result_tables[[1]] %>% filter(year=="2002") %>% filter(distribution %in% c("exponential", "powerlaw"))) , mapping = aes(x=log(x), y=log(y), color=distribution, linetype=distribution)) + theme_minimal() + ylim(-7.5,0)

```

$~$

$~$


#### Lognormal and weibull distribution versus power law (optimal tail length)

```{r, fig.show="hold", out.width="50%"}

ggplot() + geom_point(data = (OutdegreesCCDF_nested %>% filter(year=="2002") %>% .$outdCCDF %>% .[[1]]), mapping = aes( x=log(outdegree), y=log(CCDF)), shape=1) + 
  geom_line(data = (Result_tables[[1]] %>% filter(year=="2002") %>% filter(distribution %in% c("lognormal", "powerlaw"))) , mapping = aes(x=log(x), y=log(y), color=distribution, linetype=distribution)) + theme_minimal()


ggplot() + geom_point(data = (OutdegreesCCDF_nested %>% filter(year=="2002") %>% .$outdCCDF %>% .[[1]]), mapping = aes( x=log(outdegree), y=log(CCDF)), shape=1) + 
  geom_line(data = (Result_tables[[1]] %>% filter(year=="2002") %>% filter(distribution %in% c("weibull", "powerlaw"))) , mapping = aes(x=log(x), y=log(y), color=distribution, linetype=distribution)) + theme_minimal()


```





